Analysis for Project

### 2021-11-14 analysis/analysis.Rmd
Remove oout of date code chunks
Move conditional prob plot to analysis.Rmd

```{r}

```

```{r}
plot_effect_scatter(model4)
```

```{r}

```

```{r}
plot_effect_point(model4)
```

>>>>

```{r}
coef_table <- calculate_cond_means(model4)

ggplot(coef_table, aes(x=term, y=estimate,
                       color=multiracial,
                       ymin=estimate-1.39*se,
                       ymax=estimate+1.39*se))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.39*se_mid,
                ymax=estimate_mid+1.39*se_mid), 
            fill="grey90", color="grey90", alpha=0.7)+
  geom_linerange(data=subset(coef_table, multiracial))+
  geom_point()+
  coord_flip()+
  facet_wrap(~mrace, ncol=3, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=c("grey40","red"))+
  scale_linetype_manual(values=c(3,1))+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="predicted probability of being behind expected grade")
```
